Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-09-19 review_article.Rmd
add references and remove word uncertainty

## Interactivety

One of the concerns of  uncertainty communication to the non-expert is fear of cognitive overload [@mcgranaghan1993cartographic] in which the the user reaches an information threshold, beyond which will not be able to make sense of the information. These concerns are not unfounded, complexity and density of representation methods appear to overwhelm novice decision makers, while experts are able to use the detail more readily when making-decisions [@cliburn2002design]. Interactivety is a design feature within modern mapping methods that can be used to incorporate additional information and complexity without overloading the user.

Interactivety enables supplementary information to be incorporated into online atlases without cluttering the display. Interactive design features found in online cancer maps include tool tip features, drop down menus, data selection, zooming and panning allow users to explore the map as they want more information and allow flexibility in the display [@HTLWM]. The use of these supports were found in various online cancer maps identified by @roberts2019communication. The controls for basic interactive features are often placed outside of the plot space [@TGA], thus the map image is updated/replaced as the user interacts with the controls. For example, changing the population age or other demographic variables. Some more advanced interactions include direct interactions with the plot via the use of overlaid tool tip features, very few cancer atlases involve these more complex selection interactivities.

>>>>

## Interactivity

One of the concerns of adding too much information to a map is the fear of cognitive overload [@mcgranaghan1993cartographic] in which the the user reaches an information threshold, beyond which will not be able to make sense of the information. These concerns are not unfounded, complexity and density of representation methods appear to overwhelm novice decision makers, while experts are able to use the detail more readily when making-decisions [@cliburn2002design]. Interactivity is a design feature within modern mapping methods that can be used to incorporate additional information and complexity without overloading the user.

Interactivity enables supplementary information to be incorporated into online atlases without cluttering the display. Interactive design features found in online cancer maps include tool tip features, drop down menus, data selection, zooming and panning allow users to explore the map as they want more information and allow flexibility in the display [@HTLWM]. The use of these supports were found in various online cancer maps identified by @roberts2019communication. The controls for basic interactive features are often placed outside of the plot space [@TGA], thus the map image is updated/replaced as the user interacts with the controls. For example, changing the population age or other demographic variables. Some more advanced interactions include direct interactions with the plot via the use of overlaid tool tip features, very few cancer atlases involve these more complex selection interactivities.
